### 2023-10-27 manuscript.tex
add instance seg figure [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/489b570261ad55cb98e2b969b432a5ddabce03ae.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/489b570261ad55cb98e2b969b432a5ddabce03ae/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/6668535747

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/6580cbd15eeeb35f8a0f5631c71e0353b84f4fb9}{MMV-Lab/im2im-paper@6580cbd}
on October 27, 2023.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/489b570261ad55cb98e2b969b432a5ddabce03ae/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/489b570261ad55cb98e2b969b432a5ddabce03ae}{MMV-Lab/im2im-paper@489b570}
on October 27, 2023.
